\edef\bstname{mlq-title-unsrt}
\begin{filecontents*}{\jobname.bib}
@article{bib1,
    Author = {C. L. Pekeris},
    Journal = {Phys. Rev.},
    Title = {Building a positron-antipositron collider},
    Pages = {1649},
    Volume = {112},
    Year = {1958}}

@article{bib1a,
    Title = {Positron-antipositron collider and reality distortion},
    Author = {C. L. Pekeris},
    Journal = {Phys. Rev.},
    Pages = {1470},
    Volume = {126},
    Year = {1962}}

@article{bib2,
    Author = {R. C. Jones},
    Journal = {J. Opt. Soc. Am.},
    Title = {The creation of the universe by heavy photon circulation},
    Pages = {799-808},
    Volume = {45},
    Year = {1955}}

@article{bib2a,
    Author = {E. C. Doerner},
    Journal = {J. Opt. Soc. Am.},
    Pages = {669--672},
    Title = {Particle emission by quantum fluctuations},
    Volume = {52},
    Year = {1962}}

@article{bib3,
    Author = {V. R. Velasco},
    Journal = {phys. stat. sol. (b)},
    Pages = {71--75},
    Title = {Electronic properties of {Fibonacci} quasi-periodic heterostructures},
    Volume = {232},
    Year = {1999}}

@book{bib4,
    Address = {Berlin},
    Author = {H. Ibach},
    Publisher = {Springer},
    Series = {Springer Series in Optical Sciences},
    Title = {Electron Energy Loss Spectrometers: The Technology of High Performance},
    Volume = {63},
    Year = {1990}}

@book{bib5,
    Address = {Reading, MA},
    Author = {D. E. Knuth},
    Edition = {second},
    Publisher = {Addison-Wesley},
    Title = {Seminumerical Algorithms, The Art of Computer Programming Vol. 2},
    Year = {1981}}

@book{bib6,
    Address = {San Francisco},
    Author = {Beno{\^{\i}}t B. Mandelbrot},
    Chapter = {5},
    Pages = {217--219},
    Publisher = {W. H. Freeman {\&} Co},
    Title = {The Fractal Geometry of Nature},
    Year = {1988}}

@book{bib7,
    Address = {Berlin},
    Editor = {G. Casati and J. Ford},
    Publisher = {Springer},
    Series = {Lecture Notes in Physics},
    Title = {Stochastic Behavior in Classical and Quantum Hamiltonian Systems},
    Volume = {93},
    Year = {1979}}

@inbook{bib8,
    Address = {New York},
    Author = {D. J. Thoules},
    Editor = {R. Prange and S. Girvin},
    Pages = {101},
    Publisher = {Springer},
    Title = {The Quantum Hall Effect},
    Year = {1987}}

@inproceedings{bib9,
    Address = {Piscataway},
    Author = {M. Xie},
    Title = {Proceedings of the 1995 {Particle} {Accelerator} {Conference}, {Dallas}, {TX}, 1995},
    Pages = {183},
    Publisher = {IEEE},
    Year = {1996}}

@inproceedings{bib10,
    Address = {Singapore},
    Author = {S. Huant and others},
    Editor = {E. M.  Anastassakis and J. D. Joannopoulos},
    Pages = {1369},
    Publisher = {World Scientific},
    Title = {Proceedings of the 20th {International} {Conference} on the {Physics} of {Semiconductors}, {Thessaloniki} 1990},
    Year = {1991}}

@phdthesis{bib11,
    Author = {S. P. Parkin},
    Title = {Tachyon singularities},
    School = {Stanford University},
    Year = {1988}}

@techreport{bib12,
    Address = {Fanstord, CA},
    Author = {T. Terrific},
    Institution = {Fanstord University, Computer Science Department},
    Title = {New Sorting Algorithms},
    Type = {Tech. Rep.},
    Year = {1977}}
\end{filecontents*}


\documentclass[mlq]{w-art}
\usepackage{times, courier}
\title{Automatic typesetting of bibliographies\\ using Bib\TeX{} and \texttt{\bstname.bst}}
\begin{document}
\maketitle

\noindent Below you see an example for a bibliography generated by
Bib\TeX{} from the bibliographical database file\linebreak
\texttt{\jobname.bib}. One may use \texttt{\jobname.bib} as a template
for some real bibliography database. Please feel free to rename and
change this file (to use it, you have to erase its data content
anyway). It will be restored the next time you run the file
\texttt{\jobname.tex} through \LaTeX, which in turn typesets
\emph{this} document.

To produce the bibliography from the database you will have to run the
latter through Bib\TeX{} along with the bibstyle \texttt{\bstname.bst}
which as usual has to be somewhere in \TeX's search path. At the
command line (using \texttt{bash}, e.g.) one would just write
\begin{quote}
\verb+bibtex {<+\emph{filename}\verb+>}+
\end{quote}
where \texttt{<}\emph{filename}\texttt{>} is the name (w/o extension)
of the main document. However, most \TeX{} frontends have some
shortcut for that. Please see the documentation of your favourite
\TeX{} program for additional information.

Finally, to incorporate the bibliography into your document please use this code:
\begin{quote}
\verb+\bibliographystyle{+\texttt{\bstname}\verb+}+\\
\verb+\bibliography{<+\emph{bibliography}\verb+>}+
\end{quote}

Here's the example:

\nocite{*}
\bibliographystyle{\bstname}
\bibliography{\jobname}
\end{document}